Market-based Mechanisms for Resource Scheduling

### 2013-12-18 paper/paper.tex
More changes.

Rather than considering our policy directly, we will work with an idealized variant.
Our policy performs an \emph{approximate} optimization in order to remain scalable (indeed, it is easy to check that the general allocation problem
is NP-hard);
in the idealized variant, we instead imagine performing each auction by selecting the \emph{exact} optimum of the scheduling policy.
Because each individual scheduling problem tends to concern a small fraction of the cluster's resources,
this is not a stretch from reality (and we can

Naturally, it is much easier to prove guarantees for the exact version: for example, it is NP-hard to be exactly Pareto efficient in realistic
situations
even if we know the preferences of every user.
This is not merely a technical problem; it means that there can be no Pareto efficient computationally tractable schedulers in general.
So the Pareto efficiency of the exact scheme which we are approximating is the best that we could hope for in general,
and to the extent that Pareto efficiency is a useful theoretical property this is the version we should establish.

@@

By the definition of our auction, the price $p_B$ exceeds user A's willingness to pay for resources $R_B$ 
(or else user A's proxy would have continued bidding and the auction would not have concluded), 
while the price $p_A$ is less than user A's willingness to pay for resources $R_A$ 
(or else user A's proxy would have stopped bidding earlier). 
In particular, user A prefers their package to user B's package. 
Since at the start of the round user A preferred their allocation at their price to user B's allocation at user B's price, 
this property also holds at the end of the round. 
In this step we rely on our assumption that user A's valuations for their own holdings do not change after the auction is announced 
(otherwise it may be possible for user A to become envious in between rounds as more information is revealed, rather than during a round of the auction). 
We note in passing that similar assumptions are required to prove that DRF is envy-free in the dynamic setting,
even in a simple rather than realistic environment.
\qed
\end{pproof}
\vspace{-8mm}
In the case of strategy-proofness we again weaken our target conditions
to a local condition: we allow users to strategically look-ahead to future
rounds in order to determine how much they are willing to pay for a particular resource,
but require that within a single round they must honestly state those preferences.
We observe that in the dynamic setting DRF is only strategy-proof in the same ``local'' sense
\begin{theorem}[Local strategy-proofness] 
Assuming that users are indifferent to changes in each others' budgets,
and that users' willingness to pay 
incorporates accurate expectations of effects on future allocations, 
the optimal behavior in our auction is to honestly declare willingness to pay.
\end{theorem}
\vspace{-7mm}
\begin{pproof}
We give the standard argument for the dominant strategy truthfulness (strategy-proofness) of Vickrey auctions. 
Indeed, suppose on the contrary 
that $B_1$ and $B_2$ are two different bids for user A; that $R_1$ and $R_2$ are the resources received after making either of these bids and $p_1$, $p_2$ are the associated prices; that $B_1$ is an honest bid; and that user A prefers $(R_2, p_2)$ to $(R_1, p_1)$.

>>>>

Rather than considering our policy directly, we will work with an idealized variant.
Our policy performs an \emph{approximate} optimization in order to remain scalable (indeed, it is easy to check that the general allocation problem
is NP-hard, and consequently that there is \emph{no} non-trivial policy that is Pareto efficient);
in the idealized variant, we instead imagine performing each auction by selecting the \emph{exact} optimum of the scheduling policy.
Naturally, it is much easier to prove guarantees for the exact version: when the scheduling problems are small or are broken up into small pieces,
this is not a significant distortion. Moreover, we can never hope for anything beyond this kind of approximate
Pareto efficiency for computational reasons, so this seems to be the theoretical property of most interest.

@@

By the definition of our auction, the price $p_B$ exceeds user A's willingness to pay for resources $R_B$ 
(or else user A's proxy would have continued bidding and the auction would not have concluded), 
while the price $p_A$ is less than user A's willingness to pay for resources $R_A$ 
(or else user A's proxy would have stopped bidding earlier). 
In particular, user A prefers their package to user B's package. 
Since at the start of the round user A preferred their allocation at their price to user B's allocation at user B's price, 
this property also holds at the end of the round. 
In this step we rely on our assumption that user A's valuations for their own holdings do not change after the auction is announced 
(otherwise it may be possible for user A to become envious in between rounds as more information is revealed, rather than during a round of the auction). 
We note in passing that similar assumptions are required to prove that DRF is envy-free in the dynamic setting,
even in a simple rather than realistic environment.
\qed
\end{pproof}
\vspace{-5mm}
In the case of strategy-proofness we again weaken our target conditions
to a local condition: we allow users to strategically look-ahead to future
rounds in order to determine how much they are willing to pay for a particular resource,
but require that within a single round they must honestly state those preferences.
We observe that in the dynamic setting DRF is only strategy-proof in the same ``local'' sense
\begin{theorem}[Local strategy-proofness] 
Assuming that users are indifferent to changes in each others' budgets,
and that users' willingness to pay 
incorporates accurate expectations of effects on future allocations, 
the optimal behavior in our auction is to honestly declare willingness to pay.
\end{theorem}
\vspace{-7mm}
\begin{pproof}
We give the standard argument for the dominant strategy truthfulness (strategy-proofness) of Vickrey auctions. 
Indeed, suppose on the contrary 
that $B_1$ and $B_2$ are two different bids for user A; that $R_1$ and $R_2$ are the resources received after making either of these bids and $p_1$, $p_2$ are the associated prices; that $B_1$ is an honest bid; and that user A prefers $(R_2, p_2)$ to $(R_1, p_1)$.
